Critical Temperature of YBCO and BSCCO Superconductors

### 2014-12-13 Draft.tex
added pics

Superconductors are materials that lose their electrical resistance when they fall below a certain temperature, called the critical temperature. We determined the critical temperatures for $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ to be $98.35\textrm{ K} \pm 7\textrm{ K}$. We found a single phase transition at $110\text{ K}\pm 9 \text{ K}$ for $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$ as well.
The critical temperatures are found by passing a fixed current through a superconducting sample and measuring the change in voltage across the sample to determine its resistance. We describe the critical temperature as the temperature halfway through the transition from non-zero resistance to zero resistance. Previous measurement of the critical temperature for YBCO gives a critical temperature of 91 K. Our critical temperature for BSCCO is in agreement with previous measurements for $n=3$ phase found in the literature. This confirms that our BSCCO consists of mainly $n=3$, as indicated in the manual that came with our samples. We also saw agreement with a gneral decrease in critical temperature with an increase in current run through the YBCO sample, however the transition was uneven and distorted, so a specific difference in critical temperature could not be determined.

@@

Superconductivity has been found to occur in elements, alloys, binary compounds, and other materials.  
Roughly 70 years after superconductivity was discovered, ceramic materials with critical temperatures above the liquid nitrogen temperature of 77 K were found.\cite{melissinos} 
These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} 
In our experiment, we look at two high temperature superconductors, $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ and $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$, where $n=1,2,\text{ or },3$. %n=3 mainly for colorado superconductor 110 Tc
The amount of oxygen in $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ determines if the material will be superconducting.\cite{colo} The critical temperature of $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ is roughly 93 K.\cite{ybcotemp}
For $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$, the critical temperature depends on the value of n.  
They are 20 K, 85 K, and 110 K, for $n=1,2,\text{ and }3$, respectively.\cite{temps}

\section{Procedure}
The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. The manual from Colorado Superconductor Inc. notes that the BSCCO samples consists of mainly $n=3$. Each superconductor  is contained in a brass casing with three pairs of leads. 
One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
The thermocouple produces a voltage when one part of the circuit has a temperature different from a reference point.
We used different methods to measure the critical temperature of the two superconductors. 
For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. The alternating current provides a more accurate reading of the voltage across the sample, because it removes any offset the voltmeter may have.
The voltage across the YBCO sample, $V_{\text{YBCO}}$, and the voltage across the thermocouple junction, $V_{T}$ were measured with two nanovoltmeters. 
The voltage across the YBCO sample was converted into a resistance reading by the nanovoltmeter.
 \textcolor{blue}{Include circuit diagrams.}

\textcolor{red}{Finally, didn't you do some measurements at other values of current? for example, 10 mA and 100 mA, in addition to 1 mA? YOu were supposed to, and I thought you had. I can't find those results anywhere in your paper. }

@@

We used a two-phase lock-in amplifier for the BSCCO experiment. An AC circuit set up for the measurement of resistance is susceptible to contributions from capacitors and inductors. 
Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used and construction of the circuit. 
The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions. Since changes in $V_{\text{BSCCO}}$ due to resistance are in phase with applied voltage and the contributions of capacitors and inductors are out of phase, our signal is just the in phase component.  
Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate an AC current with an RMS amplitude of approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source with an RMS amplitude of 1 V.

@@

In order to determine the critical temperature, we located the point along the transition period curve that was halfway between the trend line for resistance during non-superconductivity and the trend line for resistance during superconductivity, and noted the corresponding temperature. The error in our voltage readings was very low (on the order of 0.000005mV). The larger error contribution is related to the width of the transition zone. Defining the positive error as the temperature point where the resistance is at 90\% of the non-superconducting edge, and the negative error as the temperature point where the resistance is at 10\% of the non-superconducting edge, we obtained a range of  91K to 100K and 94K to 101K, for each trial respectively. This yields a final result of $T_{C}=98.03\textrm{K}\pm7\textrm{K}$ and $T_{C}=98.67\textrm{K}\pm4.67\textrm{K}$, respectively (using the greater of the positive and negative error to be conservative).

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{ybco_sand_warmup_116_resistance_vs_temp.png}
\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between. Data was gathered every 20 seconds during warm-up.}
\label{YBCOplot1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{ybco_sand_warmup_1111_resistance_vs_temp.png}
\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between. Data was gathered every 30 seconds until onset of superconductivity, then every couple seconds throughout the transition period.}
\label{YBCOplot2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{100ma_current_ybco_critical_temperature}
\caption{Plot of resistor voltage vs temperature for a current of 100mA during transition from superconducting to non-superconducting.}
\label{100mA}
\end{figure}

Despite troubles with rebound at higher currents, a video of the transition from superconducting to non-superconducting at a current of 100mA was obtained, and is shown in Fig \ref{100mA}. While the shaped following the rebound is distorted, and it is hard to identify a single point as the critical temperature – given the double curve effect – the 1mA YBCO trial is superconducting above 90K while the 100mA the sample has already begun the transition and has left pure superconducting by 90K.

@@

Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded. Graphical analysis yielded a critical temperature for YBCO of 98.35K $\pm$ 7K and for BSCCO of 110K $pm$ 9K. According to the Colorado Superconductor Inc manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error. The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures. The general formula is $\text{Bi}_{2,1}\text{Sr}_{n+1}\text{Ca}_{\text{n}-1}\text{Cu}_{\text{n}}\text{O}_{2n+4+\delta}$. While the sample we had was specified for $n=3$, it is quite possible that other variations were present in our sample, each with their own critical temperature: $T_C$ for $n=1$ is 80K and $T_C$ for $n=2$ is 90K. \cite{colo} While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone. Finally, looking at the transition for YBCO with a current of 100mA, despite problems identifying a strict number for the critical temperature, the transition to non-superconducting clearly happens at a lower temperature then for 1mA. This is consistent with expectations since more energy from the increased current means that less thermal energy from warming up is needed to impart enough energy to stop the superconducting state within the YBCO crystals.

>>>>

Superconductors are materials that lose their electrical resistance when they fall below a certain temperature, called the critical temperature. We determined the critical temperatures for $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ to be $98.35\textrm{ K} \pm 7\textrm{ K}$. We found a single phase transition at $110\text{ K}\pm 9 \text{ K}$ for $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$ as well.
The critical temperatures are found by passing a fixed current through a superconducting sample and measuring the change in voltage across the sample to determine its resistance. We describe the critical temperature as the temperature halfway through the transition from non-zero resistance to zero resistance. 
Previous measurement of the critical temperature for YBCO gives a critical temperature of 91 K. Our critical temperature for BSCCO is in agreement with previous measurements for $n=3$ phase found in the literature. 
This confirms that our BSCCO consists of mainly $n=3$, as indicated in the manual that came with our samples. 
We also saw agreement with a general decrease in critical temperature with an increase in current run through the YBCO sample, however the transition was uneven and distorted, so a specific difference in critical temperature could not be determined.

@@

Superconductivity has been found to occur in elements, alloys, binary compounds, and other materials.  
Roughly 70 years after superconductivity was discovered, ceramic materials with critical temperatures above the liquid nitrogen temperature of 77 K were found.\cite{melissinos} 
These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} 
In our experiment, we look at two high temperature superconductors, $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ and $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$, where $n=1,2,\text{ or },3$. The amount of oxygen in $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ determines if the material will be superconducting.\cite{colo} The critical temperature of $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ is roughly 93 K.\cite{ybcotemp}
For $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$, the critical temperature depends on the value of n.  
They are 20 K, 85 K, and 110 K, for $n=1,2,\text{ and }3$, respectively.\cite{temps}

\section{Procedure}
The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. The manual from Colorado Superconductor Inc. notes that the BSCCO samples consists of mainly $n=3$. Each superconductor  is contained in a brass casing with three pairs of leads. 
One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
The thermocouple produces a voltage when one part of the circuit has a temperature different from a reference point.
We used different methods to measure the critical temperature of the two superconductors. 
For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. The alternating current provides a more accurate reading of the voltage across the sample, because it removes any offset the voltmeter may have.
The voltage across the YBCO sample, $V_{\text{YBCO}}$, and the voltage across the thermocouple junction, $V_{T}$ were measured with two nanovoltmeters. Figure \ref{ybco} shows the setup for this experiment.
The voltage across the YBCO sample was converted into a resistance reading by the nanovoltmeter.

\begin{figure}
\includegraphics[trim=1cm 3cm 1cm 1cm,clip=true,scale=0.6]{circuit1.png}
\caption{A circuit diagram of the YBCO experiment.}
\label{ybco}
\end{figure}

@@

We used a two-phase lock-in amplifier for the BSCCO experiment, as shown in Figure \ref{bscco}. An AC circuit set up for the measurement of resistance is susceptible to contributions from capacitors and inductors. 
Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used and construction of the circuit. 
The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions. Since changes in $V_{\text{BSCCO}}$ due to resistance are in phase with applied voltage and the contributions of capacitors and inductors are out of phase, our signal is just the in phase component.  
Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate an AC current with an RMS amplitude of approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source with an RMS amplitude of 1 V.

\begin{figure}
\includegraphics[trim=0cm 0cm 0cm 1cm,clip=true,scale=0.6]{circuit2.png}
\caption{A circuit diagram of the BSCCO experiment.}
\label{bscco}
\end{figure}

@@

In order to determine the critical temperature, we located the point along the transition period curve that was halfway between the trend line for resistance during non-superconductivity and the trend line for resistance during superconductivity, and noted the corresponding temperature. The error in our voltage readings was very low (on the order of 0.000005mV). The larger error contribution is related to the width of the transition zone. Defining the positive error as the temperature point where the resistance is at 90\% of the non-superconducting edge, and the negative error as the temperature point where the resistance is at 10\% of the non-superconducting edge, we obtained a range of  91K to 100K and 94K to 101K, for each trial respectively. This yields a final result of $T_{C}=98\pm7\textrm{K}$ and $T_{C}=99\textrm{K}\pm5\textrm{K}$, respectively (using the greater of the positive and negative error to be conservative).

Despite troubles with rebound at higher currents, a video of the transition from superconducting to non-superconducting at a current of 100mA was obtained, and is shown in Fig \ref{100mA}. While the shaped following the rebound is distorted, and it is hard to identify a single point as the critical temperatureâ given the double curve effectâ the 1mA YBCO trial is superconducting above 90K while the 100mA the sample has already begun the transition and has left pure superconducting by 90K.

\begin{figure}[hb!]
\centering
\includegraphics[width=7in]{ybco_sand_warmup_116_resistance_vs_temp.png}
\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between. Data was gathered every 20 seconds during warm-up.}
\label{YBCOplot1}
\end{figure}

\begin{figure}[hb!]
\centering
\includegraphics[width=7in]{ybco_sand_warmup_1111_resistance_vs_temp.png}
\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between. Data was gathered every 30 seconds until onset of superconductivity, then every couple seconds throughout the transition period.}
\label{YBCOplot2}
\end{figure}

\begin{figure}[hb!]
\centering
\includegraphics[width=7in]{100ma_current_ybco_critical_temperature}
\caption{Plot of resistor voltage vs temperature for a current of 100mA during transition from superconducting to non-superconducting.}
\label{100mA}
\end{figure}

@@

Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded. Graphical analysis yielded a critical temperature for YBCO of 98.35K $\pm$ 7K and for BSCCO of 110K $\pm$ 9K. According to the Colorado Superconductor Inc manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error. The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures. The general formula is $\text{Bi}_{2,1}\text{Sr}_{n+1}\text{Ca}_{\text{n}-1}\text{Cu}_{\text{n}}\text{O}_{2n+4+\delta}$. While the sample we had was specified for $n=3$, it is quite possible that other variations were present in our sample, each with their own critical temperature: $T_C$ for $n=1$ is 80K and $T_C$ for $n=2$ is 90K. \cite{colo} While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone. Finally, looking at the transition for YBCO with a current of 100mA, despite problems identifying a strict number for the critical temperature, the transition to non-superconducting clearly happens at a lower temperature then for 1mA. This is consistent with expectations since more energy from the increased current means that less thermal energy from warming up is needed to impart enough energy to stop the superconducting state within the YBCO crystals.
